Efficiently Handling Guards in the Low Level Design of RPython's tracing JIT

### 2012-07-27 talk/vmil2012/paper.tex
update os version for the machine running the benchmarks

The following analysis is based on a selection of benchmarks taken from the set
of benchmarks used to measure the performance of PyPy as can be seen
on.\footnote{http://speed.pypy.org/} The benchmarks were taken from the PyPy benchmarks
repository using revision
\texttt{ff7b35837d0f}.\footnote{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}
The benchmarks were run on a version of PyPy based on the
tag~\texttt{release-1.9} and patched to collect additional data about the
guards in the machine code
backends.\footnote{https://bitbucket.org/pypy/pypy/src/release-1.9} All
benchmark data was collected on a MacBook Pro 64 bit running Max OS 10.7.4 with
the loop unrolling optimization disabled.\footnote{Since loop unrolling
duplicates the body of loops it would no longer be possible to meaningfully
compare the number of operations before and after optimization. Loop unrolling
is most effective for numeric kernels, so the benchmarks presented here are not
affected much by its absence.}

>>>>

The following analysis is based on a selection of benchmarks taken from the set
of benchmarks used to measure the performance of PyPy as can be seen
on.\footnote{http://speed.pypy.org/} The benchmarks were taken from the PyPy benchmarks
repository using revision
\texttt{ff7b35837d0f}.\footnote{https://bitbucket.org/pypy/benchmarks/src/ff7b35837d0f}
The benchmarks were run on a version of PyPy based on the
tag~\texttt{release-1.9} and patched to collect additional data about the
guards in the machine code
backends.\footnote{https://bitbucket.org/pypy/pypy/src/release-1.9} All
benchmark data was collected on a MacBook Pro 64 bit running Max OS 10.8 with
the loop unrolling optimization disabled.\footnote{Since loop unrolling
duplicates the body of loops it would no longer be possible to meaningfully
compare the number of operations before and after optimization. Loop unrolling
is most effective for numeric kernels, so the benchmarks presented here are not
affected much by its absence.}
